Methodology for Assessing the State of the Practice for Domain X

### 2020-11-24 StateOfPractice/Methodology/Methodology.tex
Updates to "How to Initially Filter the Software List" section

If the list of software is too long (over around 30 packages), then steps need
to be taken to create a more manageable list. To reduce the length of the list,
the following filters are applied in the priority order listed, stopping once
a manageable number of projects is reached:

\begin{enumerate}
\item Scope: The functionality of the domain software should be increasingly
  specific.
\item Usage: The installation procedure should appear to be clear or easy to
  figure out.
\item Age: Ideally the latest release or source code commit should be relatively
  recent for software in the domain unless the candidate software appears to be
  well recommended and currently in use.
\end{enumerate}

>>>>

If the list of software is too long (over around 30 packages), then steps need
to be taken to create a more manageable list. To reduce the length of the list,
the following filters are applied.  The filters are applied in the priority
order listed, with the filtering process stopped once the list size is
manageable.

\begin{enumerate}
\item Scope: Software is removed by narrowing what functionality is considered
  to be within the scope of the domain.
\item Usage: Software packages are eliminated if their installation procedure is
  not clear and easy to follow.
\item Age: The older software packages (age being measured by the last date when
  a change was made) are eliminated, except in the cases where an older software
  package appears to be highly recommended and currently in use.
\end{enumerate}
